---
title: "ggplot_hook" # Set the document title
author: "James Muguro" # Set the author's name
date: "2022-09-18" # Set the document date
output: html_document # Specify the output format as an HTML document
  self_contained: true  # Embed external resources in the HTML document
---

## Setting up the environment
Notes: Setting up my R environment by loading the 'tidyverse' and 'Palmer penguins' packages.

```{r loading packages, echo=FALSE, warning=TRUE}
library(tidyverse)
library(palmerpenguins)
```

## Previewing our data
Here we will have a preview of our peguins dataset

```{r}
data(penguins)
View(penguins)
```

## Visualizations
Here we go through a series of visualizations

### Flipper length and body mass in purple
Here we plot flipper length against body mass

```{r visualize flipper length and body mass in purple}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g),color="Purple")
```


### Flipper and body mass by species
Here we plot flipper length against body mass and look at the breakdown by species

```{r species}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g,)) + 
  geom_point(aes(shape=species))
```

### Flipper length and body mass by species and sex
Here we plot flipper length against body mass and look at the breakdown by species and sex

```{r species and sex}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g,)) + 
  geom_point(aes(color=species,
                 shape=species))+
  facet_wrap(~sex)
```

